Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
small thing

\subsection{Supervised learning on image data sets}
\label{sec:image}
Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
We report accuracy (ACC), NLPD, and expected calibration error (ECE).
For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
fix the number of inducing points $M=1024$.
For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
In this setting, we must rely on our GP's predictive mean.
% Other approaches, \cite{immer2021improving} never inten
% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.

>>>>

\subsection{Supervised learning on image data sets}
\label{sec:image}
Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
We report accuracy (ACC), NLPD, and expected calibration error (ECE).
For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
fix the number of inducing points $M=1024$.
For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \cref{sec:sequential}.
In this setting, we must rely on our GP's predictive mean.
% Other approaches, \cite{immer2021improving} never inten
% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
